\huge A Usability Evaluation of Tor Launcher

### 2016-11-03 pets2017-paper/pets2017-paper.tex
write some of formative results.

We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser, a participant who heard of it, and multiple participants who never heard of or used it.

@@

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotheses we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Observations and Interviews} 
{\color {blue}
We give a summary of all participants here!  Quotations come from live transcription and are not necessarily verbatim.

@@

%TODO: re-watch the videos and get the exact times.

A summary about what we have seen in E1. Just put the high level takeaways so 
that people don't really need to read the summaries. Observations in E1:

%P2(regular): E1 (~1:52) 
\pquote{P1 (success, connection time, configuration time)}{summary of what they did here.}

%P3(regular): E1 (N/A; lost chunk of video… but ~1 minute) 
\pquote{P2 (success, connection time, configuration time)}{summary of what they did here.}

%P4(regular): E1 (~4:30)
\pquote{P3 (success, connection time, configuration time)}{summary of what they did here.}

%P9 (regular): E1 (~0:45)
\pquote{P4 (success, connection time, configuration time)}{summary of what they did here.}

%P10 (has used Tor before): E1 (GET TIME)
\pquote{P5 (success, connection time, configuration time)}{summary of what they did here.}

A summary about what we have seen in E2. Just put the high level takeaways so 
that people don't really need to read the summaries. Observations in E2:

%P7 (heard of Tor): E2 (~4:30) 
\pquote{P6 (success, connection time, configuration time)}{summary of what they did here.}

%P8 (used Tor): E2 (clock drift mission impossible, never succeeds) 
\pquote{P7 (success, connection time, configuration time)}{summary of what they did here.}

%P11 (used Tor before): E2 (~3:00)
\pquote{P8 (success, connection time, configuration time)}{summary of what they did here.}

%P12 (regular): E2 (GET TIME)
\pquote{P9 (success, connection time, configuration time)}{summary of what they did here.}

%P13 (regular): E2 (GET TIME) 
\pquote{P10 (success, connection time, configuration time)}{summary of what they did here.}

A summary about what we have seen in E3. Just put the high level takeaways so 
that people don't really need to read the summaries. Observations in E3:

%P1 (heard of tor before): E3 (~8:30) 
\pquote{P11 (success, connection time, configuration time)}{summary of what they did here.}

@@

%\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
%\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
%\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
%\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
%When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
%%The progress bar has a bug that causes it to update only when the level of progress increases.
%%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
%\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
%\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
%\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}

\subsection{Pain Points in Tor Launcher} 
{\color {blue}
LIST `EM! 
}

>>>>

We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser before.

@@

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotgit heses we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Results} 
We give a summary of what our participants did below. We watched the screen recording to summerize their actions and referred to their interviews for insight into why they took specific actions.

@@

%TODO: re-watch the videos and get the exact times. 
%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos

In E1, any connection to Tor will work. Bridges and proxies are optional.  
Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants configured bridges that they did not need. 
Observations in E1:

%P9 (regular): E1 (0:39; 4:49 to 5:28)
\pquote{P1 (new user, direct, 0:39)}{They clicked connect on the first screen almost immediately.}

%P2(regular): E1 (1:20, 0:22 to 1:42) 
\pquote{P2 (new user, direct, 1:20)}{They spent time reading all the text on the start screen, and clicked connect. They chose to connect directly because they were intimidated by the other option.}

%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
\pquote{P3 (previous Tor user, obfs3, 1:02)}{They clicked configure and connected with the recommended bridge.}

%P3(regular): E1 (N/A; 5:47 to 6:26) 
\pquote{P4 (new user, obfs3, ~1:39)}{They clicked configure and connected with the recommended bridge. They were going to use a proxy, but decided not to when they saw the proxy input fields.}

%P4(regular): E1 (8:56, 7:22 to 16:18)
\pquote{P5 (new user, obfs4, 8:56)}{They clicked configure, chose the recommended bridge, and then tried to configure a proxy. After not being able to fill out the proxy input fields, they go back to the bridge screen, select the obfs4 bridge, and make a connection without a proxy.}

In E2, a bridge is required to connect, but any bridge will work. Proxies are optional. 
Participants in E2 usually tried a direct connection before {\it eventually} trying the recommended bridge. Participants spent a fair bit of time trying to answer bridge and proxy questions and trying to configure proxies. 
Observations in E2:

%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
\pquote{P6 (new user, obfs3, 4:04)}{They click connect and wait three minutes before giving up on the direct connection. They then clicked configure and connected with the recommended bridge, because it was the next easiest thing to do.}

%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
\pquote{P7 (previous Tor user, obfs3, 4:08)}{They clicked connect and made a direct connection. Then, they clicked configure, answered no to both bridge and proxy questions, and effectively made another direct connection. After that, they go back to the bridge screen and finally connect with the recommended bridge.}

%P13 (regular): E2 (7:48; 0:34 to 9:22) 
\pquote{P8 (new user, obfs3, 9:22)}{They clicked connect to make a direct connection. When that did not work, they restarted Tor Launcher and made another direct connection--and repeated this three times. On the fourth restart, they decided to configure a proxy, but gave up. On the fifth restart, they connect with the recommended bridge.}

%P12 (regular): E2 (10:40; 0:46 to 11:26)
\pquote{P9 (new user, direct, 10:40)}{They clicked configure, but answer no to both bridge and proxy questions and made a direct connection, which fails. They then look at proxy settings, get intimidated, and try the direct connection again, which fails. They look for proxy settings and tried configuring a proxy for 4 minutes, but give up and try a diret connection again, which worked. This was not supposed to work, but new public relays came online after we ran our firewall rules and they connected using those relays.}

%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
\pquote{P10 (previous Tor user, failed to connect)}{They clicked connect to make a direct connection, then they made a connection with the recommended bridge (~5:42), which should have worked. However, our setup experienced a clock drift. Tor does not allow connections with bad clocks, so they could not connect to Tor unless they fixed the clock. The interface did not display an error for the clock drift, and they spent the rest of their time trying different bridges and proxies in vain.}

{\color {blue}
In E3, a bridge is required to connect, but only meek bridges work. Proxies are optional. 
Summary of E3 connections. 
Observations in E3:

%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
\pquote{P11 (success, 7:31)}{The participant tries connecting directy to the Tor network and connecting to the Tor network with an obfs3 bridge, both of which do not connect to Tor E3. Eventually, the participant selects a bridge that will connect to Tor (meek-azure), but was convinced that it would not work because it was taking too slow. They go back to the first page and click connect, which uses the configured meek-azure bridge. The participant thought that they had connected to Tor directly, and did not realize that the connect button uses whatever settings are toggled in the interface.}

@@

@@

\subsection{Pain Points in Tor Launcher} 
{\color {blue}
A summary about what we have seen in E1, E2, E3. How to fix it. 
Use some quotes here, and say insights from the interview. 
Quotations come from live transcription and are not necessarily verbatim.

%\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
%\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
%\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
%\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
%When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
%%The progress bar has a bug that causes it to update only when the level of progress increases.
%%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
%\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
%\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
%\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
}
